*flippant* -- An R package for the automated analysis of dithionite scramblase

### 2015-10-05 inst/manuscript/manuscript.rmd
One more edit-request by RJC;

##Scramblase Assay Analysis
Plotting protein to phospholipid ratio (PPR) against the likelihood for a given
proteoliposome to contain one or more scramblases, the PPR plot is at the heart 
of the analysis of dithionite scramblase assays, allowing for the visual 
comparison of specific scramblase activity between interrogated experimental 
series, which may, for example, be representative of protein preparations including 
mutant protein forms or crude extracts with or without depletion of a candidate
scramblase. 
```{r, code = formatR::usage('scramblaseAssayPlot'), eval = FALSE}
```
allows for the complete generation of the PPR plot in publication quality from 
the user assembled spreadsheet of input data (`x`), including automatically 
added graphical representations the PPR value equal to the fit constant 
$\alpha$, which implies all liposomes on average carrying one scramblase and 63%
have one or more [i.e. are active; @goren_constitutive_2014]. The behavior of the 
function may be adjusted to use scramblase-mediated fluorescence reduction 
normalized to either the maximum measurement in the series (`scaleTo = "data"`)
or the plateau of an exponential fit to it (`scaleTo = "model"`; for reasoning
see above) and whether or not to require the exponential curve fitted to the 
data to go through the origin.

>>>>

##Scramblase Assay Analysis
Plotting protein to phospholipid ratio (PPR) against the likelihood for a given
proteoliposome to contain one or more scramblases, the PPR plot is at the heart 
of the analysis of dithionite scramblase assays, allowing for the visual 
comparison of specific scramblase activity between interrogated experimental 
series, which may, for example, be representative of protein preparations including 
mutant protein forms or crude extracts with or without depletion of a candidate
scramblase. 
```{r, code = formatR::usage('scramblaseAssayPlot'), eval = FALSE}
```
allows for the complete generation of the PPR plot in publication quality from 
the user assembled spreadsheet of input data (`x`), including automatically 
added graphical representations the PPR value equal to the fit constant 
$\alpha$ ($P_{\geq 1} = 1 - e^{-1}$), which implies all liposomes on average 
carrying one scramblase and 63% have one or more 
[i.e. are active; @goren_constitutive_2014]. The behavior of the function may be
adjusted to use scramblase-mediated fluorescence reduction normalized to either
the maximum measurement in the series (`scaleTo = "data"`) or the plateau of an
exponential fit to it (`scaleTo = "model"`; for reasoning see above) and whether
or not to require the exponential curve fitted to the data to go through the
origin.
